IOI-Onset Analysis for Performing-Dynamics performances

### 2020-05-20 material/analysis/expression/stim_d/ioi_onset.Rmd
add ioi-onset, duration analyses
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'IOI-Onset Analysis for Performing-Articulation performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
dt_onset <- fread("../filtered/data_correct_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error <- fread("../filtered/data_error_correction_onset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_onset$RowNr <- rep(1:72, nrow(dt_onset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_onset <- dt_onset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only articulation
dt_ioi <- dt_onset[Condition == "performing" & Skill == "articulation"]

@@

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Performing-Articulation")
p_ioi
```

@@

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi[EighthNote == "Yes"], aes(x = normIOI)) +
  geom_histogram(binwidth = .05, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Performing-Articulation")
p_ioi_dis
```

>>>>

---
title: 'IOI-Onset Analysis for Performing-Dynamics performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

```{r extract, include = FALSE}
dt_onset <- fread("../filtered/data_correct_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv
dt_error <- fread("../filtered/data_error_correction_onset.csv", header = T, sep = ",", dec = ".") # read an error csv
# assign RowNr
dt_onset$RowNr <- rep(1:72, nrow(dt_onset)/72)
# sort by SubNr, BlockNr, TrialNr and NoteNr
dt_onset <- dt_onset[order(SubNr, BlockNr, TrialNr, RowNr),]
# include only dynamics
dt_ioi <- dt_onset[Condition == "performing" & Skill == "dynamics"]

@@

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Performing-Dynamics")
p_ioi
```

@@

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi[EighthNote == "Yes"], aes(x = normIOI)) +
  geom_histogram(binwidth = .05, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Performing-Dynamics")
p_ioi_dis
```
